\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{tabls}
\usepackage{afterpage}
\usepackage{epsf}
\usepackage{color}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{lmodern}
\usepackage{lipsum}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage[titletoc]{appendix}
% necessary commands
\newcommand{\chig}{\chi_\rg}
\newcommand{\sn}{S$_N$}
\newcommand{\varphigp}{\varphi_{\rg'}}
\newcommand{\varphig}{\varphi_\rg}
\newcommand{\need}[1]{\textcolor{red}{#1}}
\newcommand{\md}{\mathcal{D}}
\newcommand{\pd}{\partial\md}
\newcommand{\mm}[1]{\mathrm{#1}}
\newcommand{\rg}{\mm{g}}
\newcommand{\mrm}{\mm{m}}
\newcommand{\rgp}{{\rg'}}

\usepackage{geometry}
\geometry{margin=1in}

\title{A Two-Grid, Nonlinear Diffusion Acceleration Method for the $S_N$ Equations with Neutron Upscattering}
\author{Marissa Ramirez Zweiger }
\date{July 27th, 2018}


\begin{document}
\pagestyle{empty}
\begin{center}
A Two-Grid, Nonlinear Diffusion Acceleration Method  \\ 
for the $S_N$ Equations with Neutron Upscattering \\
\vspace{20mm}
by \\
\vspace{5mm}
Marissa Ramirez Zweiger \\ 
\vspace{20mm}
A thesis submitted in partial
satisfaction of the \\
\vspace{5mm}
requirements for the degree of \\
\vspace{5mm}
Master of Science \\
\vspace{5mm}
in \\
\vspace{5mm}
Nuclear Engineering \\
\vspace{5mm}
in the \\
\vspace{5mm}
Graduate Division \\
\vspace{5mm}
of the \\
\vspace{5mm}
University of California, Berkeley \\
\vspace{20mm}
Committee in charge: \\
\vspace{5mm}
Professor Rachel Slaybaugh, Chair \\
Professor Phillip Colella \\
Professor Massimiliano Fratoni \\
\vspace{5mm}
Summer 2018
\end{center}




\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
\pagenumbering{roman}
\thispagestyle{plain}
I would like to acknowledge my advisers, Dr. Rachel Slaybaugh and Dr. Phillip Colella, as well as my third committee member, Dr. Max Fratoni, for their guidance. This work would not have been possible without the mentorship of Dr. Weixiong Zheng - Thank you. I am also particularly appreciative of my colleagues, Joshua Rehak and Mario Ortega who were always willing to talk through concepts and let me bounce ideas off of them. 

Most of all, my gratitude goes to my family. Thank you to my mother, Andrea Ramirez, who has always been a constant source of support and to my partner in all things, Marcell Vazquez-Chanlatte, for always having handy the things I've needed most: useful python tricks, a blackboard, and a warm cup of tea. 
\end{abstract}
\setcounter{page}{2}
\pagestyle{plain}
\tableofcontents

\renewcommand{\abstractname}{Abstract}
\begin{abstract}
\pagenumbering{arabic}
\thispagestyle{plain}
Nonlinear diffusion acceleration (NDA), also known as coarse-mesh finite difference, is a well-known technique applied to accelerate the scattering convergence in neutronics calculations. In multigroup problems, NDA is effective in conjunction with Gauss-Seidel iteration in energy when there is not much upscattering. However, in the presence of significant upscattering, particularly when there is little leakage or absorption, which is common in thermal reactor problems, the efficiency of Gauss-Seidel with NDA degrades.
For use with other transport formulations, a two-grid (TG) acceleration scheme was developed to remedy the issue in Gauss Seidel with upscattering. It approximates iteration error by solving a one-group diffusion-like equation with artificial material properties generated by using the scattering eigen-spectrum. Inspired by this work, we derive a two-grid scheme specific for the NDA equation with Gauss-Seidel iteration.
\end{abstract}

\chapter{Introduction}
\setcounter{page}{2}
\pagestyle{plain}
\pagenumbering{arabic}
\label{sec:intro}
\input{ch-introduction.tex}


\chapter{Two-Grid, Nonlinear Diffusion Acceleration}
\label{sec:derivation}
\input{ch-derivation.tex}

\chapter{Iterative Solvers}
\label{sec:iterative}
\input{ch-iterative.tex}

\chapter{Numerical Results}
\label{sec:results}
\input{ch-results.tex}

\chapter{Conclusion \& Future Work}
\label{sec:future}
\input{ch-future.tex}

\begin{appendices}
  \chapter{FEM on an Unstructured Triangular Grid}
  \label{sec:spatial}
  \input{ch-spatial.tex}
\end{appendices}

\bibliography{mybibfile.bib}
\bibliographystyle{plain}
\end{document}
